Are We Reusing Outdated and License-Violating Code Snippets from Stack Overflow?

### 2017-02-11 cloneoverflow-latex/cloneoverflow.tex
We are writing in english, not italian...
Updated the license violation section

\usepackage[utf8]{inputenc}
\usepackage[italian]{babel}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{graphics}
\usepackage{listings}  
\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\usepackage{multirow}
%\usepackage[table]{xcolor}
\usepackage{float}
\usepackage{array}
\usepackage{ragged2e}
\usepackage{cleveref}
\usepackage{subcaption}
\usepackage{tikz}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.6\linewidth]{classification_process}
	\caption{Online code clone classification process}
	\label{fig:classification_process}
\end{figure}

@@

\begin{table}
	\centering
	\caption{Classification results of agreed and disagreed clone pairs.}
	\label{tab:classification_good_o}
	\small
	\resizebox{\columnwidth}{!}{%
		\begin{tabular}{l|r|r|r|r|r|r|r|r}
			\hline
			Set & QS & SQ & UD & EX & BP & IN & AC & Total \\ 
			\hline
			\multirow{1}{*}{\textit{good}}  & 3 & 0 & 11 & 4 & 111  & 7 & 2,172 & 2,308 \\
			\multirow{1}{*}{\textit{ok}}  & 12 & 0 & 40 & 23 & 11,547 & 22 & 105 & 11,749 \\
			\multirow{1}{*}{$S_D$} & 86 & 0 & 294 & 145 & 17,074 & 74 & 128 & 17,801 \\
			\multirow{1}{*}{$N_D$} & 9  & 0 & 35 & 6 & 17 & 8 & 13 & 88 \\ 
			\hline
			Total & 110 & 0 & 380 & 178 & 28,749 & 111 & 2,418 & 31,946 \\ 
			\hline
		\end{tabular} 
	}
\end{table}

@@

\textbf{For RQ3, our results show that more than half (62) of QS clone pairs on Stack Overflow are outdated. 59 pairs differ from their newest versions by modifications applied to variable names or method names, added or deleted statements, to a fully rewritten code with new method signatures. 3 pairs are dead snippets. They do not exist any more in the latest version. These outdated Stack Overflow online clone snippets are questionable for reuse.} %These changes did not reflect They might later find out that the copied code does not work any more due to different API versions. Even worse, they might also introduce bugs or vulnerabilities into their software.  }
%Usually when developers reuse a code snippet from a Stack Overflow post and find that it does not work nor compatible with their environment. They can cast a down vote to that answer resulting in low votes for the answer (which might be outdated). However, if the answer is marked as accepted by the person who asks the question, the check mark symbol attached to the answer is still attractive to naive developers who are ignorant.

@@

			34 & 7504040 & 29-Sep-11 & junit & 4.11 & ExternalResource.java & 4 & 23 & 11-Oct-12 & \textit{sm} & 25-Jun-16 \\
			35 & 8802082 & 10-Jan-12 & junit & 4.11 & ExpectException.java (2 overlaps) & 11 & 29 & 11-Oct-12 & \textit{sm} & 25-May-14 \\
			37 & 12593810 & 26-Sep-12 & poi & 3.6 & WorkbookFactory.java & 18 & 28 & 7-Dec-09 & \textit{rw} & 26-Jun-13 \\
			38 & 20913543 & 6-Jan-14 & spring & 3.0.5  & AutowireUtils.java & 32 & 42 & 20-Oct-10 & \textit{sm} & 28-Oct-14 \\
			39 & 18623736 & 4-Sep-13 & spring & 3.0.5  & CustomCollectionEditor.java & 33 & 71 & 20-Oct-10 & \textit{sm} & 21-Nov-13 \\
			40 & 22865824 & 4-Apr-14 & spring & 3.0.5  & JavaMailSenderImpl.java & 169 & 185 & 20-Oct-10 & \textit{sm} & 6-Oct-14 \\
			41 & 22865824 & 4-Apr-14 & spring & 3.0.5  & JavaMailSenderImpl.java & 186 & 197 & 20-Oct-10 & \textit{sm} & 6-Oct-14 \\
			42 & 20421869 & 6-Dec-13 & spring & 3.0.5  & ClassPathScanningCandidateComponent\newline Provider.java (2 overlaps) & 85 & 133 & 20-Oct-10 & \textit{rw} & 12-Aug-16 \\
			44 & 3751463 & 20-Sep-10 & spring & 3.0.5  & ScheduledTasksBeanDefinitionParser.java & 42 & 52 & 20-Oct-10 & \textit{sm} & 21-May-12 \\
			45 & 6149818 & 27-May-11 & spring & 3.0.5  & DefaultPropertiesPersister.java & 69 & 80 & 20-Oct-10 & \textit{sm} & 19-Mar-13 \\
			46 & 10952561 & 8-Jun-12 & spring & 3.0.5  & HibernateTemplate.java & 761 & 769 & 20-Oct-10 & \textit{sm} & 9-May-15 \\
			47 & 10952561 & 8-Jun-12 & spring & 3.0.5  & Jaxb2Marshaller.java & 253 & 269 & 20-Oct-10 & \textit{sm} & 28-Aug-12 \\
			48 & 20996373 & 8-Jan-14 & spring & 3.0.5  & test/../DelegatingServletInputStream.java & 6 & 20 & 20-Oct-10 & \textit{sm} & 18-Dec-08 \\
			49 & 20996373 & 8-Jan-14 & spring & 3.0.5  & web/../DelegatingServletInputStream.java & 6 & 20 & 20-Oct-10 & \textit{sm} & 15-Jul-16 \\
			50 & 20996373 & 8-Jan-14 & spring & 3.0.5  & servlet/../ DelegatingServletInputStream.java & 6 & 20 & 20-Oct-10 & \textit{sm} & 15-Jul-16 \\
			51 & 5660519 & 15-Apr-11 & spring & 3.0.5 & AnnotationMethodHandlerExceptionResolver.java & 224 & 233 & 20-Oct-10 & \textit{fd} & 20-Jan-12 \\
			52 & 4781746 & 24-Jan-11 & spring & 3.0.5  & DispatcherServlet.java & 91 & 103 & 20-Oct-10 & \textit{sm} & 8-Aug-11 \\
			53 & 3758110 & 21-Sep-10 & spring & 3.0.5  & DefaultAnnotationHandlerMapping.java & 78 & 92 & 20-Oct-10 & \textit{fd} & 20-Jan-12 \\
			54 & 9003314 & 25-Jan-12 & spring & 3.0.5  & WebDataBinder.java & 95 & 108 & 20-Oct-10 & \textit{fd} & 15-Aug-10 \\
			55 & 14019840 & 24-Dec-12 & struts2 & 2.2.1  & DefaultActionMapper.java & 128 & 144 & 17-Jul-10 & \textit{sm} & 18-Oct-13 \\
			56 & 15131432 & 28-Feb-13 & struts2 & 2.2.1  & FreemarkerManager.java & 163 & 177 & 17-Jul-10 & \textit{sm} & 28-Oct-13 \\
			57 & 15110171 & 27-Feb-13 & struts2 & 2.2.1  & StringLengthFieldValidator.java & 25 & 42 & 17-Jul-10 & \textit{sm} & 15-Jun-15 \\
			58 & 21734562 & 12-Feb-14 & tomcat & 7.0.2  & BasicAuthenticator.java (2 overlaps) & 25 & 73 & 4-Aug-10 & \textit{rw} & 4-Aug-16 \\
			60 & 21734562 & 12-Feb-14 & tomcat & 7.0.2  & FormAuthenticator.java & 51 & 61 & 4-Aug-10 & \textit{rw} & 4-Aug-16 \\
			61 & 24404964 & 25-Jun-14 & tomcat & 7.0.2  & CoyoteAdapter.java & 543 & 553 & 4-Aug-10 & \textit{sm} & 25-Sep-14 \\
			62 & 10289462 & 23-Apr-12 & tomcat & 7.0.2  & JspRuntimeLibrary.java & 252 & 296 & 4-Aug-10 & \textit{sm} & 12-Sep-12 \\

@@

\begin{table}
	\centering
	\caption{14 Qualitas projects with the highest number of true clones on Stack Overflow with their respective licenses}
	\label{t:q_projects_license}
	%	\resizebox{\columnwidth}{!}{%
	\small
	\begin{tabular}{l|r|p{4cm}}
		\hline 
		Project & Version & Licenses (no.~of files) \\
		\hline
		%		apache-ant & 1.8.4 & Apache2.0 \\
		%		apache-log4j & 1.2.16 & \\
		aspectj & 1.6.9 & Apache-1.1 (182), CPLv1 (3), \newline EPLv1 (2011), None (23), \newline SeeFile (6), Unknown (286) \\
		\hline
		eclipse-SDK &  4.1 & Apache-2 (2183), \newline BSD3NoWarranty (107), \newline CDDLorGPLv2 (296), \newline EPLv1 (18823), MPLv1.1 (93), \newline None (224), SeeFile (8), \newline spdxBSD3 (185), \newline spdxMIT (1), Unknown (714) \\
		\hline
		hadoop & 1.0.0 & Apache-2 (1,935), \newline spxdBSD/Apache-2 (8) \newline None (33), Unknown (14) \\
		\hline
		hibernate & 4.2.2 & Apache-2 (20), \newline LGPLv2.1+ (31) \newline PublicDomain (1), \newline None (1,850), SeeFile (4), \newline Unknown (4,324) \\
		\hline
		jasperreports & 3.7.4 & LGPLv2.1+ (3), \newline LGPLv3+ (1,581), \newline None (1), Unknown (4)\\
		\hline
		jfreechart & 1.0.13 & LGPLv2.1+ (989) \\
		\hline
		jgraph & 5.13.0.0 & LGPLv2.1+ (4), \newline spdxBSD (2), Unknown (151), \newline None (24), SeeFile (9) \\
		\hline
		%		jgrapht & 0.8.1 & LGPL 2.1 \& Eclipse  1.0 \\
		jstock & 1.0.7c & LGPLv2.1+ (1), \newline GPLv2+ (239), \newline Apache-2 (1), BSD3 (1), \newline None (23), SeeFile (1), \newline spdxMIT (3), Unknown (5)\\
		\hline
		jung2 & 2-0-1 & N/A \\
		\hline
		junit & 4.11 & None (160), Unknown (4)  \\
		\hline
		poi & 3.6 & Apache-2 (2,002), None (5) \\
		\hline
		spring & 3.0.5 & Apache-2 (2,982) \\
		\hline
		struts2 & 2.2.1-all & Apache-2 (1,717), \newline spdxBSD3 (6), \newline None (118), SeeFile (1), \newline Unknown (2) \\
		\hline
		tomcat & 7.0.2 & Apache-2 (1,313), None (11) \\
		%		weka & 3-7-9 & \\
		\hline
	\end{tabular} %
	%	}
\end{table}

\begin{table}[]
	\centering
	\caption{Licenses of 523 clone pairs in category A, B, and C}
	\label{tab:license_abc}
	\small
	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{p{1.5cm}|l|p{2.2cm}|r|r|r}
		\hline
		Type                                           & SO          & Qualitas          	& A & B & C \\
		\hline
		No license \newline (\textit{NL})  & None        & None           &  18 & 62 & 5 \\
		\hline
		Compatible  							 & Apache2     & Apache2  	   &  0 & 1 & 0 \\
		License	   						             & EPLv1       & EPLv1                 &  14 &  6 & 0 \\
		(\textit{CL})													& None        & CC BY 3.0   &  0 & 12 & 0 \\
		\hline
	    Incompat. 								   & None       & Apache2  						& 41 & 29 & 3 \\
		License								         & None        & BSD/BSD3                      & 0 & 64 & 0 \\
		(\textit{IL}) 								 & None        & CDDLorGPLv2                & 0 & 63 & 4 \\
															& None        & EPLv1                               & 0 & 33 & 0\\
															& None        & GPLv2/2+/3+                  &  5 & 52 & 14 \\
															& None        & LGPL2.1+/3+                   &  18 & 33 & 2 \\
															& None        & AGPLv3/3+                     & 0 & 9 &1  \\
															& None        & MPLv1\_1                         & 0 & 1 & 0\\
															& None        & spdxBSD3                      & 0 & 8 & 1 \\
															& None        & Unidentifiable                 & 0 & 1 & 0 \\
															& Proprietary & None                            & 0 & 21 & 1 \\
															& BSD3        & GPLv2+							& 0 & 1 & 0 \\
		\hline
		\multicolumn{3}{l|}{Total} 	       																&  96 & 396 & 31 \\
		\hline
	\end{tabular} %
}
\end{table}

\begin{figure*}
	\minipage{0.32\textwidth}
	\includegraphics[width=\linewidth]{heatmap_a}
	\caption*{(1) QS clones}\label{fig:heatmap_a}
	\endminipage\hspace{0.3cm}
	\minipage{0.32\textwidth}
	\includegraphics[width=\linewidth]{heatmap_b}
	\caption*{(2) UD clones}\label{fig:heatmap_b}
	\endminipage\hfill
	\minipage{0.32\textwidth}%
	\includegraphics[width=\linewidth]{heatmap_c}
	\caption*{(3) EX clones}\label{fig:heatmap_c}
	\endminipage
	\caption{Licensing between Stack Overflow code snippets and Qualitas Java file of QS, UD, and EX online clone files}
\end{figure*}

In our study, we reveal another possible situation of software licensing issues caused by code cloning ``to Stack Overflow''. We found with evidence that 110 pieces of code had been copied from 19 Qualitas projects to Stack Overflow as examples. They are also marked as accepted answers which increased their chances of being reused. The 19 open source projects came with their respective software licenses (shown in \Cref{t:q_projects_license}). However, we found that the licensing information were mostly stripped from these clones after they were posted on Stack Overflow. The licensing terms on the top of source code are not copied because mostly a small part of the file was cloned to Stack Overflow. If developers copy and reuse these licensed pieces of code in their projects, conflicts may happen without their realisation.

>>>>

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{graphics}
\usepackage{listings}  
\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\usepackage{multirow}
%\usepackage[table]{xcolor}
\usepackage{float}
\usepackage{array}
\usepackage{ragged2e}
\usepackage{cleveref}
\usepackage{subcaption}
\usepackage{tikz}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{classification_process}
	\caption{Online code clone classification process}
	\label{fig:classification_process}
\end{figure}

@@

\begin{table}
	\centering
	\caption{Classification results of agreed and disagreed clone pairs.}
	\label{tab:classification_good_o}
	\small
	\resizebox{\columnwidth}{!}{%
		\begin{tabular}{l|r|r|r|r|r|r|r|r}
			\hline
			Set & QS & SQ & UD & EX & BP & IN & AC & Total \\ 
			\hline
			\multirow{1}{*}{\textit{good}}  & 3 & 0 & 11 & 4 & 111  & 7 & 2,172 & 2,308 \\
			\multirow{1}{*}{\textit{ok}}  & 14 & 0 & 40 & 21 & 11,547 & 22 & 105 & 11,749 \\
			\multirow{1}{*}{$S_D$} & 86 & 0 & 294 & 145 & 17,074 & 74 & 128 & 17,801 \\
			\multirow{1}{*}{$N_D$} & 9  & 0 & 35 & 6 & 17 & 8 & 13 & 88 \\ 
			\hline
			Total & 112 & 0 & 380 & 176 & 28,749 & 111 & 2,418 & 31,946 \\ 
			\hline
		\end{tabular} 
	}
\end{table}

@@

\textbf{For RQ3, our results show that more than half (64) of QS clone pairs on Stack Overflow are outdated. 60 pairs differ from their newest versions by modifications applied to variable names or method names, added or deleted statements, to a fully rewritten code with new method signatures. 4 pairs are dead snippets. They do not exist any more in the latest version. These outdated Stack Overflow online clone snippets are questionable for reuse.} %These changes did not reflect They might later find out that the copied code does not work any more due to different API versions. Even worse, they might also introduce bugs or vulnerabilities into their software.  }
%Usually when developers reuse a code snippet from a Stack Overflow post and find that it does not work nor compatible with their environment. They can cast a down vote to that answer resulting in low votes for the answer (which might be outdated). However, if the answer is marked as accepted by the person who asks the question, the check mark symbol attached to the answer is still attractive to naive developers who are ignorant.

@@

			34 & 7504040 & 29-Sep-11 & junit & 4.11 & ExternalResource.java (3 overlaps) & 4 & 23 & 11-Oct-12 & \textit{sm} & 25-Jun-16 \\
			37 & 8802082 & 10-Jan-12 & junit & 4.11 & ExpectException.java (2 overlaps) & 11 & 29 & 11-Oct-12 & \textit{sm} & 25-May-14 \\
			39 & 12593810 & 26-Sep-12 & poi & 3.6 & WorkbookFactory.java & 18 & 28 & 7-Dec-09 & \textit{rw} & 26-Jun-13 \\
			40 & 20913543 & 6-Jan-14 & spring & 3.0.5  & AutowireUtils.java & 32 & 42 & 20-Oct-10 & \textit{sm} & 28-Oct-14 \\
			41 & 18623736 & 4-Sep-13 & spring & 3.0.5  & CustomCollectionEditor.java & 33 & 71 & 20-Oct-10 & \textit{sm} & 21-Nov-13 \\
			42 & 22865824 & 4-Apr-14 & spring & 3.0.5  & JavaMailSenderImpl.java & 169 & 185 & 20-Oct-10 & \textit{sm} & 6-Oct-14 \\
			43 & 22865824 & 4-Apr-14 & spring & 3.0.5  & JavaMailSenderImpl.java & 186 & 197 & 20-Oct-10 & \textit{sm} & 6-Oct-14 \\
			44 & 20421869 & 6-Dec-13 & spring & 3.0.5  & ClassPathScanningCandidateComponent\newline Provider.java (2 overlaps) & 85 & 133 & 20-Oct-10 & \textit{rw} & 12-Aug-16 \\
			46 & 3751463 & 20-Sep-10 & spring & 3.0.5  & ScheduledTasksBeanDefinitionParser.java & 42 & 52 & 20-Oct-10 & \textit{sm} & 21-May-12 \\
			47 & 6149818 & 27-May-11 & spring & 3.0.5  & DefaultPropertiesPersister.java & 69 & 80 & 20-Oct-10 & \textit{sm} & 19-Mar-13 \\
			48 & 10952561 & 8-Jun-12 & spring & 3.0.5  & HibernateTemplate.java & 761 & 769 & 20-Oct-10 & \textit{sm} & 9-May-15 \\
			49 & 10952561 & 8-Jun-12 & spring & 3.0.5  & Jaxb2Marshaller.java & 253 & 269 & 20-Oct-10 & \textit{sm} & 28-Aug-12 \\
			50 & 20996373 & 8-Jan-14 & spring & 3.0.5  & test/../DelegatingServletInputStream.java & 6 & 20 & 20-Oct-10 & \textit{sm} & 18-Dec-08 \\
			51 & 20996373 & 8-Jan-14 & spring & 3.0.5  & web/../DelegatingServletInputStream.java & 6 & 20 & 20-Oct-10 & \textit{sm} & 15-Jul-16 \\
			52 & 20996373 & 8-Jan-14 & spring & 3.0.5  & servlet/../ DelegatingServletInputStream.java & 6 & 20 & 20-Oct-10 & \textit{sm} & 15-Jul-16 \\
			53 & 5660519 & 15-Apr-11 & spring & 3.0.5 & AnnotationMethodHandlerExceptionResolver.java & 224 & 233 & 20-Oct-10 & \textit{fd} & 20-Jan-12 \\
			54 & 4781746 & 24-Jan-11 & spring & 3.0.5  & DispatcherServlet.java & 91 & 103 & 20-Oct-10 & \textit{sm} & 8-Aug-11 \\
			55 & 3758110 & 21-Sep-10 & spring & 3.0.5  & DefaultAnnotationHandlerMapping.java & 78 & 92 & 20-Oct-10 & \textit{fd} & 20-Jan-12 \\
			56 & 9003314 & 25-Jan-12 & spring & 3.0.5  & WebDataBinder.java & 95 & 108 & 20-Oct-10 & \textit{fd} & 15-Aug-10 \\
			57 & 14019840 & 24-Dec-12 & struts2 & 2.2.1  & DefaultActionMapper.java & 128 & 144 & 17-Jul-10 & \textit{sm} & 18-Oct-13 \\
			58 & 15131432 & 28-Feb-13 & struts2 & 2.2.1  & FreemarkerManager.java & 163 & 177 & 17-Jul-10 & \textit{sm} & 28-Oct-13 \\
			59 & 15110171 & 27-Feb-13 & struts2 & 2.2.1  & StringLengthFieldValidator.java & 25 & 42 & 17-Jul-10 & \textit{sm} & 15-Jun-15 \\
			60 & 21734562 & 12-Feb-14 & tomcat & 7.0.2  & BasicAuthenticator.java (2 overlaps) & 25 & 73 & 4-Aug-10 & \textit{rw} & 4-Aug-16 \\
			62 & 21734562 & 12-Feb-14 & tomcat & 7.0.2  & FormAuthenticator.java & 51 & 61 & 4-Aug-10 & \textit{rw} & 4-Aug-16 \\
			63 & 24404964 & 25-Jun-14 & tomcat & 7.0.2  & CoyoteAdapter.java & 543 & 553 & 4-Aug-10 & \textit{sm} & 25-Sep-14 \\
			64 & 10289462 & 23-Apr-12 & tomcat & 7.0.2  & JspRuntimeLibrary.java & 252 & 296 & 4-Aug-10 & \textit{sm} & 12-Sep-12 \\

@@

\begin{table}
	\centering
	\caption{Licenses of online clones (file-level) from Qualitas projects}
	\label{t:q_projects_license}
	%	\resizebox{\columnwidth}{!}{%
	\small
	\begin{tabular}{l|l|r|r|r}
		\hline 
		Project & License & QS & UD & Total \\
		\hline
		netbeans &  CDDLorGPLv2 &  & 57 & 57 \\
		&  N/A &  & 8 & 8 \\
		&  spdxBSD3 &  & 6 & 6 \\
		&  MPLv1.1 &  & 1 & 1 \\
		&  unknown &  & 1 & 1 \\
		\hline
		jung2 &  BSD3 & 2 & 27 & 29 \\
		\hline
		eclipse-SDK & EPLv1 & 6 & 11 & 17 \\
		& CDDLorGPLv2 & 1 & 1 & 2 \\
		&  Apache-2 &  & 1 & 1 \\
		& N/A & 1 &  & 1 \\
		& unknown &  & 1 & 1 \\
		\hline
		hibernate & LesserGPLv2.1+ & 18 & 4 & 22 \\
		\hline
		spring & Apache-2 & 18 & 2 & 20 \\
		\hline
		vuze & GPLv2 &  & 11 & 11 \\
		\hline
		jstock & GPLv2+ &  & 9 & 9 \\
		& unknown &  & 1 & 1 \\
		\hline
		tomcat & Apache-2 & 5 & 5 & 10 \\
		\hline
		hadoop & Apache-2 & 8 &  & 8 \\
		& N/A & 1 &  & 1 \\
		\hline
		jfreechart & LesserGPLv2.1+ & 3 & 5 & 8 \\
		\hline
	\end{tabular} %
	%	}
\end{table}

\begin{table}[]
	\centering
	\caption{License matching of online clones (file-level) in QS, UD, and EX}
	\label{tab:license_abc}
	\small
	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{p{2cm}|l|p{2.2cm}|r|r|r}
		\hline
		Type & Stack Overflow & Qualitas & QS & UD & EX \\
		\hline
		No license (\textit{NL})  & None & None &  5 & 22 & 4 \\
		\hline
		Compatible & Apache2 & Apache2 &  0 & 1 & 0 \\
		License	& EPLv1 & EPLv1 &  1 & 1 & 0 \\
		(\textit{CL}) & N/A & CC BY 3.0   &  0 & 0 & 5 \\
		\hline
	    Incompat. & BSD3 & GPLv2+ & 0 & 1 & 0 \\
		License	& N/A & AGPLv3/3+ & 1 & 2 & 0 \\
		(\textit{IL}) & N/A & Apache-2 & 41 & 23 & 5 \\
		& N/A & BSD3 & 3 & 28 & 4 \\
		& N/A & CDDL or GPLv2 & 1 & 58 & 0 \\
		& N/A & CDDLv1 & 0 & 0 & 1 \\
		& N/A & EPLv1 & 7 & 10 & 0 \\
		& N/A & GPLv2/2+/3+ & 2 & 32 & 62 \\
		& N/A & LGPLv2/2.1+/3+ & 24 & 32 & 0 \\
		& N/A & MPLv1.1 & 0 & 1 & 0 \\
		& N/A & spdxBSD3 & 0 & 10 & 0 \\
		& N/A & SPLv1 & 0 & 0 & 1 \\
		& N/A & unknown & 0 & 3 & 3 \\
		& spdxBSD3 & AGPLv3+ & 0 & 2 & 0 \\
		& unknown & MIT-like & 0 & 0 & 1 \\
		& unknown & Sun & 0 & 0 & 1 \\
		\hline
		\multicolumn{3}{l|}{Total} &  85 & 226 & 87 \\
		\hline
	\end{tabular} %
}
\end{table}

\begin{figure*}
		\centering
		\begin{minipage}{.4\textwidth}
			\centering
			\includegraphics[width=\linewidth]{heatmap_a}
			\caption*{(1) QS clones}\label{fig:heatmap_a}
		\end{minipage}%
		\hspace{5ex}
		\begin{minipage}{0.4\textwidth}
			\centering
			\includegraphics[width=\linewidth]{heatmap_c}
			\caption*{(2) EX clones}\label{fig:heatmap_c}
		\end{minipage}
	\caption{License mapping of QS and EX online clones}
\end{figure*}

In our study, we reveal another possible situation of software licensing issues caused by code cloning ``to Stack Overflow''. We found with evidence that 112 pieces of code had been copied from 19 Qualitas projects to Stack Overflow as examples. They are also marked as accepted answers which increased their chances of being reused. The projects came with their respective software licenses (shown in \Cref{t:q_projects_license}). However, we found that the licensing information were mostly stripped from these clones after they were posted on Stack Overflow. The licensing terms on the top of source code are not copied because mostly a small part of the file was cloned to Stack Overflow. If developers copy and reuse these licensed pieces of code in their projects, conflicts may happen without their realisation.
